---
title: "Uni-Students-Moodle-App-Views-Responses-"
author: "Calopez, Camayodo, Octaviano"
date: "2024-04-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

// load the excel file

```{r}
#install.packages("readr")
#install.packages("dplyr")
library(readr)
library(dplyr)

uni_students_satisfaction <- read_csv("Uni-Students-Moodle-App-Views-Responses.csv")

head(uni_students_satisfaction)
summary(uni_students_satisfaction)  
View(uni_students_satisfaction)
```

// columns of questions

```{r}

question_columns <- c("U6", "RA1", "RA5", "OE7", "EOU3", "EOUS", "EOU6", "EU4", "A1", "AF1", "AF2", "Affect1", "SN1", "SN2", "SF2", "SF4", "PBC2", "PBC3", "PBC5", "FC3", "SE1", "SE4", "SE6", "SE7", "ANX1", "ANX2", "ANX3", "ANX4", "BI1", "BI2", "BI3")

```

```{r}

# Change questions column to factor
for (name in question_columns) {
  uni_students_satisfaction[[column_name]] <- factor(uni_students_satisfaction[[name]],
                              levels = c("1", "2", "3", "4", "5"),
                              ordered = TRUE)
}

```


```{r}

View(uni_students_satisfaction)

```

//age
```{r}
library(dplyr)

respondents_age <- uni_students_satisfaction %>%
  summarize(
    total_count = n(),                # Total count of records
    mean_age = mean(age, na.rm = TRUE),        # Mean age
    median_age = median(age, na.rm = TRUE),    # Median age
    min_age = min(age, na.rm = TRUE),          # Minimum age
    max_age = max(age, na.rm = TRUE)           # Maximum age
  )

respondents_age

ggplot(uni_students_satisfaction, aes(x = age)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, size = 3, color = "black") + # Add count numbers
  labs(title = "Distribution of Age",
       x = "Age",
       y = "Frequency") +
  scale_x_continuous(breaks = seq(18, 26, by = 1)) +
  theme_minimal()


```


//sex
```{r}
ggplot(uni_students_satisfaction, aes(x = sex, fill = sex)) +
  geom_bar() +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, size = 3, color = "black") + # Add count numbers
  labs(title = "Distribution of Sex",
       x = "Sex",
       y = "Frequency") +
  theme_minimal()


```


U6: How helpful do you think the Moodle app would be for your studies?
```{r}
library(dplyr)

U6_response_counts <- uni_students_satisfaction %>%
  count(U6)

U6_response_counts

library(ggplot2)

ggplot(U6_response_counts, aes(x = U6, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question U6",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

RA1: Do you believe the Moodle app would make completing tasks easier for you?
```{r}
library(dplyr)

RA1_response_counts <- uni_students_satisfaction %>%
  count(RA1)

RA1_response_counts

library(ggplot2)

ggplot(RA1_response_counts, aes(x = RA1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question RA1",
       x = "Response",
       y = "Count") +
  theme_minimal()

```


RA5: Will using the Moodle app improve your productivity as a student?
```{r}
library(dplyr)

RA5_response_counts <- uni_students_satisfaction %>%
  count(RA5)

RA5_response_counts

library(ggplot2)

ggplot(RA5_response_counts, aes(x = RA5, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question RA5",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

OE7: Would using the Moodle app motivate you to do better academically?
```{r}
library(dplyr)

OE7_response_counts <- uni_students_satisfaction %>%
  count(OE7)

OE7_response_counts

library(ggplot2)

ggplot(OE7_response_counts, aes(x = OE7, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question OE7",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

EOU5: Do you expect to find the Moodle app easy to navigate?
```{r}
library(dplyr)

EOU5_response_counts <- uni_students_satisfaction %>%
  count(EOU5)

EOU5_response_counts

library(ggplot2)

ggplot(EOU5_response_counts, aes(x = EOU5, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EOU5",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

EOU6: How confident are you in your ability to learn to use the Moodle app effectively?
```{r}
library(dplyr)

EOU6_response_counts <- uni_students_satisfaction %>%
  count(EOU6)

EOU6_response_counts

library(ggplot2)

ggplot(EOU6_response_counts, aes(x = EOU6, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EOU6",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

EU4: Would you consider the Moodle app user-friendly?
```{r}
library(dplyr)

EU4_response_counts <- uni_students_satisfaction %>%
  count(EU4)

EOU6_response_counts

library(ggplot2)

ggplot(EU4_response_counts, aes(x = EU4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EU4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

A1: Do you think learning to use the Moodle app would be easy for you?
```{r}
library(dplyr)

A1_response_counts <- uni_students_satisfaction %>%
  count(A1)

A1_response_counts

library(ggplot2)

ggplot(A1_response_counts, aes(x = A1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question A1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

AF1: What do you think about including the Moodle app in your daily academic routine?
```{r}
library(dplyr)

AF1_response_counts <- uni_students_satisfaction %>%
  count(AF1)

AF1_response_counts

library(ggplot2)

ggplot(AF1_response_counts, aes(x = AF1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question AF1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

AF2: Will the Moodle app make your learning experience more interesting?
```{r}
library(dplyr)

AF2_response_counts <- uni_students_satisfaction %>%
  count(AF2)

AF2_response_counts

library(ggplot2)

ggplot(AF2_response_counts, aes(x = AF2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question AF2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

Affect1: Would using the Moodle app make your academic tasks more enjoyable?
```{r}
library(dplyr)

Affect1_response_counts <- uni_students_satisfaction %>%
  count(Affect1)

Affect1_response_counts

library(ggplot2)

ggplot(Affect1_response_counts, aes(x = Affect1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question Affect1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SN1: How positive do you feel about using the Moodle app?
```{r}
library(dplyr)

SN1_response_counts <- uni_students_satisfaction %>%
  count(SN1)

SN1_response_counts

library(ggplot2)

ggplot(SN1_response_counts, aes(x = SN1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SN1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SN2: How much do others influence your decision to use the Moodle app?
```{r}
library(dplyr)

SN2_response_counts <- uni_students_satisfaction %>%
  count(SN2)

SN2_response_counts

library(ggplot2)

ggplot(SN2_response_counts, aes(x = SN2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SN2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SF2: How important is it to you that your peers support using the Moodle app?
```{r}
library(dplyr)

SF2_response_counts <- uni_students_satisfaction %>%
  count(SF2)

SF2_response_counts

library(ggplot2)

ggplot(SF2_response_counts, aes(x = SF2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SF2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SF4: Has the university's encouragement influenced your view of the Moodle app?
```{r}
library(dplyr)

SF4_response_counts <- uni_students_satisfaction %>%
  count(SF4)

SF4_response_counts

library(ggplot2)

ggplot(SF4_response_counts, aes(x = SF4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SF4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

PBC2: How supportive do you find the university's administration in promoting the use of the Moodle app?
```{r}
library(dplyr)

PBC2_response_counts <- uni_students_satisfaction %>%
  count(PBC2)

PBC2_response_counts

library(ggplot2)

ggplot(PBC2_response_counts, aes(x = PBC2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question PBC2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

PBC3: Do you think you have everything you need to use the Moodle app effectively?
```{r}
library(dplyr)

PBC3_response_counts <- uni_students_satisfaction %>%
  count(PBC3)

PBC3_response_counts

library(ggplot2)

ggplot(PBC3_response_counts, aes(x = PBC3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question PBC3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

FC3: Do you feel confident in your knowledge of how to use the Moodle app?
```{r}
library(dplyr)

FC3_response_counts <- uni_students_satisfaction %>%
  count(FC3)

FC3_response_counts

library(ggplot2)

ggplot(FC3_response_counts, aes(x = FC3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question FC3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE1: Have you faced any issues using the Moodle app with other systems?
```{r}
library(dplyr)

SE1_response_counts <- uni_students_satisfaction %>%
  count(SE1)

SE1_response_counts

library(ggplot2)

ggplot(SE1_response_counts, aes(x = SE1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE4: How easy is it to get help if you encounter problems with the Moodle app?
```{r}
library(dplyr)

SE4_response_counts <- uni_students_satisfaction %>%
  count(SE4)

SE4_response_counts

library(ggplot2)

ggplot(SE4_response_counts, aes(x = SE4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE6: How confident are you in your ability to use the Moodle app on your own?
```{r}
library(dplyr)

SE6_response_counts <- uni_students_satisfaction %>%
  count(SE6)

SE6_response_counts

library(ggplot2)

ggplot(SE6_response_counts, aes(x = SE6, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE6",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE7: Would you feel comfortable asking for help if you needed it while using the Moodle app?
```{r}
library(dplyr)

SE7_response_counts <- uni_students_satisfaction %>%
  count(SE7)

SE7_response_counts

library(ggplot2)

ggplot(SE7_response_counts, aes(x = SE7, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE7",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX1: Do you think having enough time would help you use the Moodle app better?
```{r}
library(dplyr)

ANX1_response_counts <- uni_students_satisfaction %>%
  count(ANX1)

ANX1_response_counts

library(ggplot2)

ggplot(ANX1_response_counts, aes(x = ANX1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX2: How helpful do you find the built-in help feature in the Moodle app?
```{r}
library(dplyr)

ANX2_response_counts <- uni_students_satisfaction %>%
  count(ANX2)

ANX2_response_counts

library(ggplot2)

ggplot(ANX2_response_counts, aes(x = ANX2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX3: Do you feel nervous about using the Moodle app?
```{r}
library(dplyr)

ANX3_response_counts <- uni_students_satisfaction %>%
  count(ANX3)

ANX3_response_counts

library(ggplot2)

ggplot(ANX3_response_counts, aes(x = ANX3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX4: How worried are you about accidentally losing information while using the Moodle app?
```{r}
library(dplyr)

ANX4_response_counts <- uni_students_satisfaction %>%
  count(ANX4)

ANX4_response_counts

library(ggplot2)

ggplot(ANX4_response_counts, aes(x = ANX4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

BI1: Would you say the Moodle app is intimidating to use?
```{r}
library(dplyr)

BI1_response_counts <- uni_students_satisfaction %>%
  count(BI1)

BI1_response_counts

library(ggplot2)

ggplot(BI1_response_counts, aes(x = BI1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question BI1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

BI2: Do you plan to start using the Moodle app in your studies within the next few months?
```{r}
library(dplyr)

BI2_response_counts <- uni_students_satisfaction %>%
  count(BI2)

BI2_response_counts

library(ggplot2)

ggplot(BI2_response_counts, aes(x = BI2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question BI2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

BI3: How likely are you to use the Moodle app for your academic work in the next few months?
```{r}
library(dplyr)

BI3_response_counts <- uni_students_satisfaction %>%
  count(BI3)

BI3_response_counts

library(ggplot2)

ggplot(BI3_response_counts, aes(x = BI3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```


EOUS: Have you already planned to integrate the Moodle app into your academic routine soon?
```{r}
library(dplyr)

EOUS_response_counts <- uni_students_satisfaction %>%
  count(EOUS)

EOUS_response_counts

library(ggplot2)

# Assuming `EOUS_response_counts` contains the counts of responses for the "EOUS" question column
ggplot(EOUS_response_counts, aes(x = EOUS, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EOUS",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

