---
title: "Uni-Students-Moodle-App-Views-Responses-"
author: "Calopez, Camayodo, Octaviano"
date: "2024-04-18"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

// load the csv file

```{r}
#install.packages("readr")
#install.packages("dplyr")
library(readr)
library(dplyr)

uni_students_satisfaction <- read_csv("Uni-Students-Moodle-App-Views-Responses.csv")

head(uni_students_satisfaction)
summary(uni_students_satisfaction)  
#View(uni_students_satisfaction)
```

// columns of questions

```{r}

question_columns <- c("U6", "RA1", "RA5", "OE7", "EOU3", "EOU5", "EOU6", "EU4", "A1", "AF1", "AF2", "Affect1", "SN1", "SN2", "SF2", "SF4", "PBC2", "PBC3", "PBC5", "FC3", "SE1", "SE4", "SE6", "SE7", "ANX1", "ANX2", "ANX3", "ANX4", "BI1", "BI2", "BI3")

```

```{r}

#View(uni_students_satisfaction)

```

//age

```{r}
library(dplyr)
library(ggplot2)
respondents_age <- uni_students_satisfaction %>%
  summarize(
    total_count = n(),                # Total count of records
    mean_age = mean(age, na.rm = TRUE),        # Mean age
    median_age = median(age, na.rm = TRUE),    # Median age
    min_age = min(age, na.rm = TRUE),          # Minimum age
    max_age = max(age, na.rm = TRUE)           # Maximum age
  )

respondents_age

ggplot(uni_students_satisfaction, aes(x = age)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, size = 3, color = "black") + # Add count numbers
  labs(title = "Distribution of Age",
       x = "Age",
       y = "Frequency") +
  scale_x_continuous(breaks = seq(18, 26, by = 1)) +
  theme_minimal()


```

//sex

```{r}
ggplot(uni_students_satisfaction, aes(x = sex, fill = sex)) +
  geom_bar() +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, size = 3, color = "black") + # Add count numbers
  labs(title = "Distribution of Sex",
       x = "Sex",
       y = "Frequency") +
  theme_minimal()


```


------------------------------------------------------------------------

```         
      Performance Expectancy:
```

------------------------------------------------------------------------

U6: How helpful do you think the Moodle app would be for your studies?

```{r}
library(dplyr)

U6_response_counts <- uni_students_satisfaction %>%
  count(U6)

U6_response_counts

library(ggplot2)

ggplot(U6_response_counts, aes(x = U6, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question U6",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

RA1: Do you believe the Moodle app would make completing tasks easier for you?

```{r}
library(dplyr)

RA1_response_counts <- uni_students_satisfaction %>%
  count(RA1)

RA1_response_counts

library(ggplot2)

ggplot(RA1_response_counts, aes(x = RA1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question RA1",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

RA5: Will using the Moodle app improve your productivity as a student?

```{r}
library(dplyr)

RA5_response_counts <- uni_students_satisfaction %>%
  count(RA5)

RA5_response_counts

library(ggplot2)

ggplot(RA5_response_counts, aes(x = RA5, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question RA5",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

OE7: Would using the Moodle app motivate you to do better academically?

```{r}
library(dplyr)

OE7_response_counts <- uni_students_satisfaction %>%
  count(OE7)

OE7_response_counts

library(ggplot2)

ggplot(OE7_response_counts, aes(x = OE7, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question OE7",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

------------------------------------------------------------------------

```         
      Effort Expectancy:
```

------------------------------------------------------------------------

EOU3: Do you expect to find the Moodle app easy to navigate?

```{r}
library(dplyr)

EOU3_response_counts <- uni_students_satisfaction %>%
  count(EOU3)

EOU3_response_counts

library(ggplot2)

ggplot(EOU3_response_counts, aes(x = EOU3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EOU3",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

EOU5: How confident are you in your ability to learn to use the Moodle app effectively?

```{r}
library(dplyr)

EOU5_response_counts <- uni_students_satisfaction %>%
  count(EOU5)

EOU5_response_counts

library(ggplot2)

ggplot(EOU5_response_counts, aes(x = EOU5, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EOU5",
       x = "Response",
       y = "Count") +
  theme_minimal()

```

EOU6: Would you consider the Moodle app user-friendly?

```{r}
library(dplyr)

EOU6_response_counts <- uni_students_satisfaction %>%
  count(EOU6)

EOU6_response_counts

library(ggplot2)

ggplot(EOU6_response_counts, aes(x = EOU6, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EOU6",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

EU4: Do you think learning to use the Moodle app would be easy for you?

```{r}
library(dplyr)

EU4_response_counts <- uni_students_satisfaction %>%
  count(EU4)

EU4_response_counts

library(ggplot2)

ggplot(EU4_response_counts, aes(x = EU4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question EU4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

------------------------------------------------------------------------

```         
      Attitude toward using technology:
```

------------------------------------------------------------------------

A1: What do you think about including the Moodle app in your daily academic routine?

```{r}
library(dplyr)

A1_response_counts <- uni_students_satisfaction %>%
  count(A1)

A1_response_counts

library(ggplot2)

ggplot(A1_response_counts, aes(x = A1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question A1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

AF1: Will the Moodle app make your learning experience more interesting?

```{r}
library(dplyr)

AF1_response_counts <- uni_students_satisfaction %>%
  count(AF1)

AF1_response_counts

library(ggplot2)

ggplot(AF1_response_counts, aes(x = AF1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question AF1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

AF2: Would using the Moodle app make your academic tasks more enjoyable?

```{r}
library(dplyr)

AF2_response_counts <- uni_students_satisfaction %>%
  count(AF2)

AF2_response_counts

library(ggplot2)

ggplot(AF2_response_counts, aes(x = AF2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question AF2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

Affect1: How positive do you feel about using the Moodle app?

```{r}
library(dplyr)

Affect1_response_counts <- uni_students_satisfaction %>%
  count(Affect1)

Affect1_response_counts

library(ggplot2)

ggplot(Affect1_response_counts, aes(x = Affect1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question Affect1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```
------------------------------------------------------------------------

```         
      Social influence:
```

------------------------------------------------------------------------

SN1: How much do others influence your decision to use the Moodle app?

```{r}
library(dplyr)

SN1_response_counts <- uni_students_satisfaction %>%
  count(SN1)

SN1_response_counts

library(ggplot2)

ggplot(SN1_response_counts, aes(x = SN1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SN1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SN2: How important is it to you that your peers support using the Moodle app?

```{r}
library(dplyr)

SN2_response_counts <- uni_students_satisfaction %>%
  count(SN2)

SN2_response_counts

library(ggplot2)

ggplot(SN2_response_counts, aes(x = SN2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SN2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SF2: Has the university's encouragement influenced your view of the Moodle app?

```{r}
library(dplyr)

SF2_response_counts <- uni_students_satisfaction %>%
  count(SF2)

SF2_response_counts

library(ggplot2)

ggplot(SF2_response_counts, aes(x = SF2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SF2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SF4: How supportive do you find the university's administration in promoting the use of the Moodle app?

```{r}
library(dplyr)

SF4_response_counts <- uni_students_satisfaction %>%
  count(SF4)

SF4_response_counts

library(ggplot2)

ggplot(SF4_response_counts, aes(x = SF4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SF4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```
------------------------------------------------------------------------

```         
      Facilitating Conditions:
```

------------------------------------------------------------------------
PBC2: Do you think you have everything you need to use the Moodle app effectively?

```{r}
library(dplyr)

PBC2_response_counts <- uni_students_satisfaction %>%
  count(PBC2)

PBC2_response_counts

library(ggplot2)

ggplot(PBC2_response_counts, aes(x = PBC2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question PBC2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

PBC3: Do you feel confident in your knowledge of how to use the Moodle app?

```{r}
library(dplyr)

PBC3_response_counts <- uni_students_satisfaction %>%
  count(PBC3)

PBC3_response_counts

library(ggplot2)

ggplot(PBC3_response_counts, aes(x = PBC3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question PBC3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

PBC5: Have you faced any issues using the Moodle app with other systems?

```{r}
library(dplyr)

PBC5_response_counts <- uni_students_satisfaction %>%
  count(PBC5)

PBC5_response_counts

library(ggplot2)

ggplot(PBC5_response_counts, aes(x = PBC5, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question PBC5",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

FC3: How easy is it to get help if you encounter problems with the Moodle app?

```{r}
library(dplyr)

FC3_response_counts <- uni_students_satisfaction %>%
  count(FC3)

FC3_response_counts

library(ggplot2)

ggplot(FC3_response_counts, aes(x = FC3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question FC3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```
------------------------------------------------------------------------

```         
      Self-Efficacy:
```

------------------------------------------------------------------------
SE1: How confident are you in your ability to use the Moodle app on your own?

```{r}
library(dplyr)

SE1_response_counts <- uni_students_satisfaction %>%
  count(SE1)

SE1_response_counts

library(ggplot2)

ggplot(SE1_response_counts, aes(x = SE1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE4: Would you feel comfortable asking for help if you needed it while using the Moodle app?

```{r}
library(dplyr)

SE4_response_counts <- uni_students_satisfaction %>%
  count(SE4)

SE4_response_counts

library(ggplot2)

ggplot(SE4_response_counts, aes(x = SE4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE6: Do you think having enough time would help you use the Moodle app better?

```{r}
library(dplyr)

SE6_response_counts <- uni_students_satisfaction %>%
  count(SE6)

SE6_response_counts

library(ggplot2)

ggplot(SE6_response_counts, aes(x = SE6, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE6",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

SE7: How helpful do you find the built-in help feature in the Moodle app?

```{r}
library(dplyr)

SE7_response_counts <- uni_students_satisfaction %>%
  count(SE7)

SE7_response_counts

library(ggplot2)

ggplot(SE7_response_counts, aes(x = SE7, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question SE7",
       x = "Response",
       y = "Count") +
  theme_minimal()
```
------------------------------------------------------------------------

```         
      Anxiety:
```

------------------------------------------------------------------------
ANX1: Do you feel nervous about using the Moodle app?

```{r}
library(dplyr)

ANX1_response_counts <- uni_students_satisfaction %>%
  count(ANX1)

ANX1_response_counts

library(ggplot2)

ggplot(ANX1_response_counts, aes(x = ANX1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX2: How worried are you about accidentally losing information while using the Moodle app?

```{r}
library(dplyr)

ANX2_response_counts <- uni_students_satisfaction %>%
  count(ANX2)

ANX2_response_counts

library(ggplot2)

ggplot(ANX2_response_counts, aes(x = ANX2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX3: Do you hesitate to use the Moodle app because you're afraid of making mistakes?

```{r}
library(dplyr)

ANX3_response_counts <- uni_students_satisfaction %>%
  count(ANX3)

ANX3_response_counts

library(ggplot2)

ggplot(ANX3_response_counts, aes(x = ANX3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

ANX4: Would you say the Moodle app is intimidating to use?

```{r}
library(dplyr)

ANX4_response_counts <- uni_students_satisfaction %>%
  count(ANX4)

ANX4_response_counts

library(ggplot2)

ggplot(ANX4_response_counts, aes(x = ANX4, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question ANX4",
       x = "Response",
       y = "Count") +
  theme_minimal()
```
------------------------------------------------------------------------

```         
     Behavioral Intention to Use the System:
```

------------------------------------------------------------------------
BI1: Do you plan to start using the Moodle app in your studies within the next few months?

```{r}
library(dplyr)

BI1_response_counts <- uni_students_satisfaction %>%
  count(BI1)

BI1_response_counts

library(ggplot2)

ggplot(BI1_response_counts, aes(x = BI1, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question BI1",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

BI2: How likely are you to use the Moodle app for your academic work in the next few months?

```{r}
library(dplyr)

BI2_response_counts <- uni_students_satisfaction %>%
  count(BI2)

BI2_response_counts

library(ggplot2)

ggplot(BI2_response_counts, aes(x = BI2, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question BI2",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

BI3: Have you already planned to integrate the Moodle app into your academic routine soon?

```{r}
library(dplyr)

BI3_response_counts <- uni_students_satisfaction %>%
  count(BI3)

BI3_response_counts

library(ggplot2)

ggplot(BI3_response_counts, aes(x = BI3, y = n)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  geom_text(aes(label = n), vjust = -0.5) +  # Add labels with count above each bar
  labs(title = "Responses for Question BI3",
       x = "Response",
       y = "Count") +
  theme_minimal()
```

```{r}
# Load the VIM package
library(VIM)

# Draw an aggregation plot of biopics
 uni_students_satisfaction%>% 
	aggr(combined = TRUE, numbers = TRUE)

```

```{r}
# Define the determinant categories and their corresponding questions
determinants <- list(
  "Performance Expectancy" = c("U6", "RA1", "RA5", "OE7"),
  "Effort Expectancy" = c("EOU3", "EOU5", "EOU6", "EU4"),
  "Attitude Toward Using Technology" = c("A1", "AF1", "AF2", "Affect1"),
  "Social Influence" = c("SN1", "SN2", "SF2", "SF4"),
  "Facilitating Conditions" = c("PBC2", "PBC3", "PBC5", "FC3"),
  "Self-Efficacy" = c("SE1", "SE4", "SE6", "SE7"),
  "Anxiety" = c("ANX1", "ANX2", "ANX3", "ANX4"),
  "Behavioral Intention to Use the System" = c("BI1", "BI2", "BI3")
)

# Initialize an empty data frame to store results
determinants_stats <- data.frame(Determinant = character(), Mean = numeric(), SD = numeric(), stringsAsFactors = FALSE)

# Loop through each determinant
for (determinant in names(determinants)) {
  # Extract questions corresponding to the determinant
  questions <- determinants[[determinant]]
  
  # Subset the dataset for the questions corresponding to the determinant
  subset_data <- uni_students_satisfaction[, questions]
  
  # Compute mean and standard deviation for each question
  means <- apply(subset_data, 2, mean, na.rm = TRUE)
  sds <- apply(subset_data, 2, sd, na.rm = TRUE)
  
  # Compute mean and standard deviation for the determinant
  determinant_mean <- mean(means)
  determinant_sd <- sd(means)
  
  # Add the determinant stats to the data frame
  determinants_stats <- rbind(determinants_stats, data.frame(Determinant = determinant, Mean = determinant_mean, SD = determinant_sd))
}

# View the resulting data frame
print(determinants_stats)


```


The results of the code provide insights into different aspects of what students think about the Moodle app. For example, it tells us about students' feelings and expectations. Performance Expectancy shows how much students believe the app is useful for their studies. Attitude Toward Using Technology reveals how students feel about using the app. Social Influence looks at how friends and school support influence students' decisions to use the app. Facilitating Conditions show if students feel confident in their technical skills and support resources. Self-Efficacy tells us if students are comfortable using the app on their own. Behavioral Intention to Use the System shows if students are willing to use the app for their studies.These insights aid in understanding students' overall perception of the app, identifying areas of confidence and potential concerns, such as anxiety despite perceived ease of use.

```{r}
library(ggplot2)


bar_colors <- c("#1f77b4", "#ff7f0e")

# Create the grouped bar plot
ggplot(determinants_stats, aes(x = Determinant, y = Mean, fill = Determinant)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9), width = 0.7) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width = 0.2, position = position_dodge(width = 0.9)) +
  labs(title = "Mean and Standard Deviation of Determinants",
       x = "Determinant",
       y = "Mean",
       fill = "Determinant") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = rep(bar_colors, length(unique(determinants_stats$Determinant)))) +
  guides(fill = FALSE)  # Hide legend for fill color


```



